%%% Seznam použité literatury je zpracován podle platných standardů. Povinnou citační
%%% normou pro diplomovou práci je ISO 690. Jména časopisů lze uvádět zkráceně, ale jen
%%% v kodifikované podobě. Všechny použité zdroje a prameny musí být řádně citovány.

\def\bibname{Bibliography}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}


%\bibitem{lamport94}
%  {\sc Lamport,} Leslie.
%  \emph{\LaTeX: A Document Preparation System}.
%  2. vydání.
%  Massachusetts: Addison Wesley, 1994.
%  ISBN 0-201-52983-1.


\bibitem{blind}
{Guo, R., Zhu, X., and Hao, Y.}
A Chinese spoken dialog system for blind men,
In: \emph{Systems, Man, and Cybernetics 2001 IEEE International Conference on},
Vol. 2, IEEE, pp. 865--868.

\bibitem{asdf}
{\sc Jurčíček, F., Dušek, O., Plátek, O., and Žilka, L.}
Alex: A Statistical Dialogue Systems Framework,
In: \emph{Text, Speech and Dialogue},
Springer International Publishing, 2014, pp. 587--594.


\bibitem{asr}
{\sc Roy, N., Pineau, J., and Thrun, S.}
Spoken dialogue management using probabilistic reasoning.
In: \emph{Proceedings of the 38th Annual Meeting on Association for Computational Linguistics}.
Association for Computational Linguistics, 2000, pp. 93--100.

\bibitem{oplatek}
{\sc Plátek, O., and Jurčíček F.}
Free on-line speech recogniser based on Kaldi ASR toolkit producing word posterior lattices,
In: \emph{15th Annual Meeting of the Special Interest Group on Discourse and Dialogue},
2014, p. 108.

\bibitem{oplatek_thesis}
{\sc Plátek, Ondřej.}
Speech recognition using KALDI,
2014.

\bibitem{mturk}
{\sc Ipeirotis, Panagiotis G., Foster Provost, and Jing Wang.}
Quality management on amazon mechanical turk,
In: \emph{Proceedings of the ACM SIGKDD workshop on human computation},
ACM, 2010, pp. 64--67.

\bibitem{slu}
{\sc Dušek, O., Plátek, O., Žilka, L., and Jurčíček, F.}
Alex: Bootstrapping a Spoken Dialogue System for a New Domain by Real Users,
In: \emph{15th Annual Meeting of the Special Interest Group on Discourse and Dialogue},
2014, pp. 79--83.

\bibitem{gtfs}
{\sc Ma, T., and Jan-Knaap, G.}
Analyzing Employment Accessibility in a Multimodal Network using GTFS: A Demonstration of the Purple Line, Maryland,
2014.

\bibitem{crowdflower}
{\sc Biewald, Lukas.}
\emph{CrowdFlower resource library}
[online]. 2015 [cit May 5, 2015].
Available from: \nolinkurl{http://www.crowdflower.com/overview}

\bibitem{ptics}
{\sc UFAL-DSG}
\emph{The Alex Dialogue Systems Framework - Public Transport Information},
[online]. 2015 [cit May 5, 2015].
Available from: \nolinkurl{http://ufal.mff.cuni.cz/alex}



% \bibitem{USARSim}
% {\sc Carpin, S., Lewis, M., Wang, J., Balakirsky, S., Scrapper, C.}
% USARSim: a robot simulator for research and education. In: \emph{Proceedings of 
% the 2007 IEEE Conference on Robotics and Automation}, 2007, pp. 1400--1405. 
% URL:  \nolinkurl{http://usarsim.sourceforge.net/}

% \bibitem{Player}
% {\sc The Player Project} \emph{Player manual} [online]. 2011 [cit July 10, 2012]. Availible from:  \nolinkurl{http://playerstage.sourceforge.net/} 

% \bibitem{Pyro}
% {\sc Blank, D.S., Kumar, D., Meeden, L., Yanco, H.} The Pyro toolkit for AI and robotics. In: \emph{AI Magzine}, Volume 27, Number 1, 2006. URL:  \nolinkurl{http://pyrorobotics.org/?page=Pyro}
 

% \bibitem{VMAC}
% {\sc Miklic, D., Bogdan, S., Kalinovcic, L.}
% A control architecture for warehouse automation - Performance evaluation in USARSim. In: \emph{Robotics and Automation (ICRA), 2011 IEEE International Conference on}, 2011, pp. 109--114. URL:
%  \nolinkurl{http://vma-competition.com/}  

\end{thebibliography}
